\begin{module}{
  moduleName=Complicated Wires,
  indexString=Complicated Wires,
  imageResource=complicated_wires.png
}
{
  These wires aren't like the others. Some have stripes! That makes them completely different. The good news is that we've found a concise set of instructions on what to do about it! Maybe too concise...
}

% Add your module content here
% This is where you'll add tables, instructions, and other module-specific content

\begin{itemize}
  \item[$\bullet$] Check the 4 sections one after another.
  \item[$\bullet$] If a section applies, cut all wires matching any of its conditions.
\end{itemize}

Hints:
\begin{itemize}
  \item[$\bullet$] \PURPLE means that the wire has both \RED and \BLUE in it.
  \item[$\bullet$] Plain \WHITE means that the wire has neither \RED nor \BLUE in it.
  \item[$\bullet$] \RED means that the wire has no \BLUE in it.
  \item[$\bullet$] \BLUE means that the wire has no \RED in it.
\end{itemize}

\begin{minipage}[t]{0.48\textwidth}
% First List - Left Column, Top
\textheading{Always:}
\begin{enumerate}
  \renewcommand{\labelenumi}{\alph{enumi}.}
  \item LED off and
  \begin{enumerate}
    \renewcommand{\labelenumii}{\roman{enumii}.}
    \item Plain \WHITE (STAR / no STAR)
    \item \RED, has STAR
  \end{enumerate}
\end{enumerate}

% Third List - Left Column, Bottom
\textheading{If there are 2+ Batteries:}
\begin{enumerate}
  \renewcommand{\labelenumi}{\alph{enumi}.}
  \item LED on and
  \begin{enumerate}
    \renewcommand{\labelenumii}{\roman{enumii}.}
    \item Plain \WHITE, has STAR
    \item \RED (STAR / no STAR)
  \end{enumerate}
\end{enumerate}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
% Second List - Right Column, Top
\textheading{If the Last Digit of the Serial Number is Even:}
\begin{enumerate}
  \renewcommand{\labelenumi}{\alph{enumi}.}
  \setcounter{enumi}{2}
  \item No STAR and
  \begin{enumerate}
    \renewcommand{\labelenumii}{\roman{enumii}.}
    \item LED off
    \item \PURPLE
  \end{enumerate}
\end{enumerate}

% Fourth List - Right Column, Bottom
\textheading{If there is a Parallel Port:}
\begin{enumerate}
  \renewcommand{\labelenumi}{\alph{enumi}.}
  \item LED on, \BLUE
  \item LED off, \PURPLE, has STAR
\end{enumerate}
\end{minipage}

\end{module}
